R Notebook

### 2020-02-11 src/comb-maxent.Rmd
adjusted kappa done. range check started

filenames <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "dis_prob_cells.csv", recursive = TRUE,full.names = TRUE)

all <- map_dfr(filenames, function(x) fread(x) %>% 
                       mutate(Month=substr(basename(x),1,3))) %>% 
  mutate(Probability = gsub(">0.9", "0.9 - 1", Probability),
         Depth = factor(round(Depth,1)),
         Depth = factor(Depth,ordered = TRUE, levels = rev(levels(Depth))),
         Month=factor(months(parse_date_time(Month,"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))))

#make the plot
  ggplot(all) +
  geom_col(aes(Depth, p_cells, fill = Probability),width=1) +
  coord_flip()+
  facet_wrap(~Month,ncol=5)+
  labs(y = "% Ocean at Depth", x = "Depth (meters)")+
  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1, guide=guide_legend(nrow=2, byrow = TRUE))+
  theme_classic()+
  theme(legend.position = "bottom", axis.text.y = element_text(size=7), strip.background = element_blank()) +
  scale_x_discrete(breaks = c(dlst[1], dlst[5], dlst[10], dlst[15], dlst[20], dlst[25], dlst[30], dlst[35], dlst[40], dlst[47]))

ggsave("../output/maxent/paper_plots/test.png", dpi = 600)
```

@@

#2d maps

this is currently set to 0.5 cut-off... not SLR and MJ would like this changed

@@

filelist <- list.files("../data/plot3-2d/hotspot-mapping/",include.dirs = TRUE)

x <- stack(file.path("../data/plot3-2d/hotspot-mapping/",filelist)) %>% 
  mask(mcp) %>% 
  rasterToPoints() %>% 
  as.data.frame() %>% 
  gather(key = "variable", value = "value",-x,-y) %>% 
  mutate(month=factor(months(parse_date_time(gsub("_.*$", "",variable),"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))),
         value=ifelse(value==1,">0.5","<0.5"))

@@

ggplot(x)+
  geom_sf(data=s,fill='grey',colour='transparent')+
  geom_raster(aes(x,y,fill=value))+
  scale_fill_manual(values=c('transparent','red'))+
  geom_sf(data=mcp,fill="transparent")+
  geom_text(data=df,x=-50,y=67,label=df$total)+
  facet_wrap(~month,nrow=2)+#,
  theme_classic()+
  scale_x_continuous(breaks = seq(-70,-50,10))+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold"))

ggsave("../output/maxent/paper_plots/two-d.png", height = 210, width = 297, units = "mm", dpi = 600)
```

>>>>

filenames <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "dis_prob_cells.csv", recursive = TRUE,full.names = TRUE)
filenames <- filenames[ !grepl("maxkap", filenames) ] #remove all the maxkap files

all <- map_dfr(filenames, function(x) fread(x) %>% 
                       mutate(Month=substr(basename(x),1,3))) %>% 
  mutate(Probability = gsub(">0.9", "0.9 - 1", Probability),
         Depth = factor(round(Depth,1)),
         Depth = factor(Depth,ordered = TRUE, levels = rev(levels(Depth))),
         Month=factor(months(parse_date_time(Month,"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))))
#create a list of depths so you can set breaks for the x-axis (which is showing as the y-axis...)
dlst <- unique(all$Depth)
dlst <- as.character(dlst)
dlst <- as.numeric(dlst)
dlst <- sort(dlst)
#make the plot
  ggplot(all) +
  geom_col(aes(Depth, p_cells, fill = Probability),width=1) +
  coord_flip()+
  facet_wrap(~Month,ncol=2)+
  labs(y = "% Ocean at Depth", x = "Depth (meters)")+
  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1, guide=guide_legend(nrow=2, byrow = TRUE))+
  theme_classic()+
  theme(legend.position = "bottom", axis.text.y = element_text(size=7), strip.background = element_blank()) +
  scale_x_discrete(breaks = c(dlst[1], dlst[5], dlst[10], dlst[15], dlst[20], dlst[25], dlst[30], dlst[35], dlst[40], dlst[47]))

ggsave("../output/maxent/paper_plots/prob_by_depth.png", width = 210, height = 297, units = "mm", dpi = 600)
```

@@

#2d maps - max kappa thresholds

this creates binary maps for each layer based on the maxkappa threshold
```{r}
binprob <- function(x){
  ifelse(x > 0 & x >= mk, 1,
  ifelse(x <= 0, 0, NA))
}

#get the maxkap value
alst <- list.files("../output/maxent/models/test-comb/", pattern = "avgAIC.csv", full.names = TRUE)

#create binary maps per depth layer
  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/hotspot_mapping/prob_by_depth/", mth, "_maxkap_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/hotspot_mapping/prob_by_depth/", mth, "_maxkap_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}

then create an summary map....
```{r >maxkap prob monthly 2D representation}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mthna <- mthord[m]
  binaryprob_list <- list.files(paste0("../output/maxent/paper_plots/hotspot_mapping/"), pattern = paste0(mthna, "*_maxkap_.*.asc$"), full.names = TRUE)
  binstack <- stack(binaryprob_list)
  stacksum <- sum(binstack, na.rm = TRUE)
  writeRaster(stacksum, paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_maxkap_2d.asc"), overwrite=TRUE)
  plot(stacksum, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_maxkap_2d.png")))
  dev.off()
}

now create summary maps where values are binary - not counts of cells
```{r}
binprob <- function(x){
  ifelse(x > 0, 1,
  ifelse(x <= 0, 0, NA))
}

  clogasc_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = "*_maxkap_2d.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- str_sub(clogasc_list[cum], start = 46, end = -8)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
```

now create a table to see how many cells there are >maxkap in each month (for editing plots)

```{r count cells >maxkap}

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = ".*_maxkap_2d.asc", full.names = TRUE)
sum2d <- data.frame(matrix(ncol = 2, nrow = 10))
sum2d <- setNames(sum2d, c("month", "count"))

for (r in 1:length(binaryprob_list)){
  ras <- raster(binaryprob_list[r])
  rnm <- names(ras)
  sum2d$month[r] <- gsub("_maxkap_2d", "", x = rnm)
  sum2d$count[r] <- cellStats(ras, sum, asSample = TRUE)
}

#order table from march to december
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
sum2d <- sum2d[match(mthord, sum2d$month), ]

#get proportion
tcs <- read.csv("../output/maxent/paper_plots/cellsperlayer.csv", header = TRUE) #file showing how many cells per depth
#tcs <- tcs[-c(1:3), ] #because the top three rows are deeper than the capelin obs...
totc <- sum(tcs$no_cells)

for (r in 1:nrow(sum2d)){
  sum2d$proportion[r] <- (sum2d$count[r]/totc)*100 #this actually shows percentage
}

write.csv(sum2d, "../output/maxent/paper_plots/cell_count_maxkap.csv", row.names = FALSE)

```{r plot maxkap 2d}
library(sf)
library(purrr)
library(raster)
library(lubridate)
library(tidyverse)

@@

filelist <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = "maxkap_single.asc", include.dirs = TRUE)

x <- stack(file.path("../output/maxent/paper_plots/hotspot_mapping/",filelist)) %>% 
  mask(mcp) %>% 
  rasterToPoints() %>% 
  as.data.frame() %>% 
  gather(key = "variable", value = "value",-x,-y) %>% 
  mutate(month=factor(months(parse_date_time(gsub("_.*$", "",variable),"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))),
         value=ifelse(value==1,">0.5","<0.5"))

@@

#quickest way might be just to inject my csv file with the correct values here....
df2 <- read.csv("../output/maxent/paper_plots/cell_count_maxkap.csv", header = TRUE)
df$total <- df2$proportion
df$total <- format(round(df$total, digits = 2))
#colnames(df) <- c("month", "cellc", "total")

ggplot(x)+
  geom_raster(aes(x,y,fill=value))+
  scale_fill_manual(values=c('light yellow','black'))+
  geom_sf(data=s,fill='grey',colour='transparent')+
  geom_sf(data=mcp,fill="transparent")+
  geom_text(data=df,x=-50,y=67,label=df$total)+
  facet_wrap(~month,nrow=2)+#,
  theme_classic()+
  scale_x_continuous(breaks = seq(-70,-50,10))+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold"))

ggsave("../output/maxent/paper_plots/maxkap_2d.png", height = 210, width = 297, units = "mm", dpi = 600)

get data to plot maxkap binary by depth... 
```{r maxkap by depth}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  ascdepth <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_maxkap.*asc"), full.names = TRUE)
  binaryavgstack <- stack(ascdepth)
  stackstathigh <- data.frame(matrix(ncol = 2, nrow = nlayers(binaryavgstack)))
  stackstathigh[ ,1] <- c(1:47)
  colnames(stackstathigh) <- c("asclayer", "prob_bin")

  for (lyr in 1:nlayers(binaryavgstack)){
    ascname <-  str_sub(ascdepth[lyr], 67, -5)
    dlay <- binaryavgstack[[lyr]]
    dlay <- calc(dlay, fun = binprob) #creates raster layer with cell values based on the binprob function
    lyrsum <- cellStats(dlay, sum)
    stackstathigh$prob_bin[lyr] <- lyrsum
    stackstathigh$asclayer[lyr] <- ascname

  }
  write.csv(stackstathigh, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

```{r percentage cells above and below maxkap}
mthord <- c("mar",  "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/cellsperlayer.csv", header = TRUE)

for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_cellcount_bydepth_avg.csv"), header = TRUE, stringsAsFactors=FALSE)
  for (r in 1:nrow(a)){
    # a$Depth[r] <- gsub("b_avg_cloglog_", "", x = a$Depth[r])
    # d1 <- str_sub(a$Depth[r], end = 4)
    d1 <- a$asclayer[r]
	  for (ro in 1:nrow(cumst1)){
      #d2 <- str_sub(cumst1$depth[ro], end = 4)
	    d2 <- cumst1$depth[ro]
      if (d1 == d2){
          a$total_cells[r] <- cumst1$no_cells[ro]
      }
	  }
    a$p_cells[r] <- (a$prob_bin[r]/a$total_cells[r])*100
    a$Probability[r] <- 1
  }
    #a$asclayer <- as.numeric(a$asclayer)

  a2 <- as.data.frame(a$asclayer)
  a2$total_cells <- a$total_cells
  a2$prob_bin <- a$total_cells - a$prob_bin
  a2$p_cells <- (a2$prob_bin/a2$total_cells)*100
  a2$Probability <- 0
  colnames(a2)[1] <- "asclayer"

  b <- rbind(a, a2)
  colnames(b)[1] <- "Depth"

  write.csv(b, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_dis_prob_cells.csv"), row.names = FALSE)
}

based on Remi's code - maxkappa derrived habitat by depth
```{r maxkappa habitat by depth}
require(data.table)
require(purrr)
require(lubridate)
require(tidyverse)
require(viridis)

filenames <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "_maxkap_dis_prob_cells.csv", recursive = TRUE,full.names = TRUE)

all <- map_dfr(filenames, function(x) fread(x) %>% 
                       mutate(Month=substr(basename(x),1,3))) %>% 
  mutate(Depth = factor(round(Depth,1)),
         Depth = factor(Depth,ordered = TRUE, levels = rev(levels(Depth))),
         Month=factor(months(parse_date_time(Month,"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))))

#make probability a factor - sam added this
all$Probability <- as.factor(all$Probability)

#make the plot
  ggplot(all) +
  geom_col(aes(Depth, p_cells, fill = Probability),width=1) +
  coord_flip()+
  facet_wrap(~Month,ncol=2)+
  labs(y = "% Ocean at Depth", x = "Depth (meters)")+
  scale_fill_manual(aesthetics = "fill", values=c('light yellow','black'))+
  theme_classic()+
  theme(legend.position = "bottom", axis.text.y = element_text(size=7), strip.background = element_blank()) +
  scale_x_discrete(breaks = c(dlst[1], dlst[5], dlst[10], dlst[15], dlst[20], dlst[25], dlst[30], dlst[35], dlst[40], dlst[47]))

ggsave("../output/maxent/paper_plots/maxkap_prob_by_depth.png", width = 210, height = 297, units = "mm", dpi = 600)
```

### 2020-02-11 src/testing_file.Rmd
adjusted kappa done. range check started

```{r}
binprob <- function(x){
  ifelse(x > 0 & x >= mk, 1,
  ifelse(x <= 0, 0, NA))
}

alst <- list.files("../output/maxent/models/test-comb/", pattern = "avgAIC.csv", full.names = TRUE)

@@

  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}

@@

get data to plot probability by depth... 
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

from here sam

```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mth <- mthord[m]
  probblst <- list.files(paste0("../output/maxent/paper_plots/prob_by_depth"), pattern = paste0("^", mth, "_probbin_.*.csv"), full.names = TRUE)
  a <- read.csv(probblst[1])
  b <- read.csv(probblst[2])
  c <- read.csv(probblst[3])
  d <- read.csv(probblst[4])
  e <- read.csv(probblst[5])
  f <- read.csv(probblst[6])
  g <- read.csv(probblst[7])
  h <- read.csv(probblst[8])
  i <- read.csv(probblst[9])
  j <- read.csv(probblst[10])

  write.csv(stackstat, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_allprobbin_cellcount_bydepth_avg.csv"), row.names = FALSE)
}

@@

>>>>

this creates binary maps based on th#max kappa thresholds

this creates binary maps based on the maxkappa threshold
```{r}
binprob <- function(x){
  ifelse(x > 0 & x >= mk, 1,
  ifelse(x <= 0, 0, NA))
}

#get the maxkap value
alst <- list.files("../output/maxent/models/test-comb/", pattern = "avgAIC.csv", full.names = TRUE)

@@

#create binary maps per depth layer
  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/hotspot_mapping/prob_by_depth/", mth, "_maxkap_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/hotspot_mapping/prob_by_depth/", mth, "_maxkap_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}

@@

then create an summary map....
```{r >maxkap prob monthly 2D representation}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mthna <- mthord[m]
  binaryprob_list <- list.files(paste0("../output/maxent/paper_plots/hotspot_mapping/"), pattern = paste0(mthna, "*_maxkap_.*.asc$"), full.names = TRUE)
  binstack <- stack(binaryprob_list)
  stacksum <- sum(binstack, na.rm = TRUE)
  writeRaster(stacksum, paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_maxkap_2d.asc"), overwrite=TRUE)
  plot(stacksum, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_maxkap_2d.png")))
  dev.off()
}

  clogasc_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = "*_maxkap_2d.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- str_sub(clogasc_list[cum], start = 46, end = -8)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
```

now create a table to see how many cells there are >maxkap in each month (for editing plots)

```{r count cells >maxkap}

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = ".*_maxkap_2d.asc", full.names = TRUE)
sum2d <- data.frame(matrix(ncol = 2, nrow = 10))
sum2d <- setNames(sum2d, c("month", "count"))

for (r in 1:length(binaryprob_list)){
  ras <- raster(binaryprob_list[r])
  rnm <- names(ras)
  sum2d$month[r] <- gsub("_maxkap_2d", "", x = rnm)
  sum2d$count[r] <- cellStats(ras, sum, asSample = TRUE)
}

write.csv(sum2d, "../output/maxent/paper_plots/cell_count_maxkap.csv", row.names = FALSE)

filelist <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = "maxkap_single.asc", include.dirs = TRUE)

x <- stack(file.path("../output/maxent/paper_plots/hotspot_mapping/",filelist)) %>% 
  mask(mcp) %>% 
  rasterToPoints() %>% 
  as.data.frame() %>% 
  gather(key = "variable", value = "value",-x,-y) %>% 
  mutate(month=factor(months(parse_date_time(gsub("_.*$", "",variable),"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))),
         value=ifelse(value==1,">0.5","<0.5"))

#quickest way might be just to inject my csv file with the correct values here....
df2 <- read.csv("../output/maxent/paper_plots/cell_count_maxkap.csv", header = TRUE)
df$total <- df2$proportion
df$total <- format(round(df$total, digits = 2))
#colnames(df) <- c("month", "cellc", "total")

ggsave("../output/maxent/paper_plots/maxkap_2d.png", height = 210, width = 297, units = "mm", dpi = 600)

e maxkappa threshold
```{r}
binprob <- function(x){
  ifelse(x > 0 & x >= mk, 1,
  ifelse(x <= 0, 0, NA))
}

#get the maxkap value
alst <- list.files("../output/maxent/models/test-comb/", pattern = "avgAIC.csv", full.names = TRUE)

#create binary maps per depth layer
  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/hotspot_mapping/prob_by_depth/", mth, "_maxkap_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/hotspot_mapping/prob_by_depth/", mth, "_maxkap_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
}

then create an summary map....
```{r >maxkap prob monthly 2D representation}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mthna <- mthord[m]
  binaryprob_list <- list.files(paste0("../output/maxent/paper_plots/hotspot_mapping/"), pattern = paste0(mthna, "*_maxkap_.*.asc$"), full.names = TRUE)
  binstack <- stack(binaryprob_list)
  stacksum <- sum(binstack, na.rm = TRUE)
  writeRaster(stacksum, paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_maxkap_2d.asc"), overwrite=TRUE)
  plot(stacksum, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_maxkap_2d.png")))
  dev.off()
}

  clogasc_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = "*_maxkap_2d.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- str_sub(clogasc_list[cum], start = 46, end = -8)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
```

now create a table to see how many cells there are >maxkap in each month (for editing plots)

```{r count cells >maxkap}

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = ".*_maxkap_2d.asc", full.names = TRUE)
sum2d <- data.frame(matrix(ncol = 2, nrow = 10))
sum2d <- setNames(sum2d, c("month", "count"))

for (r in 1:length(binaryprob_list)){
  ras <- raster(binaryprob_list[r])
  rnm <- names(ras)
  sum2d$month[r] <- gsub("_maxkap_2d", "", x = rnm)
  sum2d$count[r] <- cellStats(ras, sum, asSample = TRUE)
}

write.csv(sum2d, "../output/maxent/paper_plots/cell_count_maxkap.csv", row.names = FALSE)

filelist <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = "maxkap_single.asc", include.dirs = TRUE)

x <- stack(file.path("../output/maxent/paper_plots/hotspot_mapping/",filelist)) %>% 
  mask(mcp) %>% 
  rasterToPoints() %>% 
  as.data.frame() %>% 
  gather(key = "variable", value = "value",-x,-y) %>% 
  mutate(month=factor(months(parse_date_time(gsub("_.*$", "",variable),"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))),
         value=ifelse(value==1,">0.5","<0.5"))

#quickest way might be just to inject my csv file with the correct values here....
df2 <- read.csv("../output/maxent/paper_plots/cell_count_maxkap.csv", header = TRUE)
df$total <- df2$proportion
df$total <- format(round(df$total, digits = 2))
#colnames(df) <- c("month", "cellc", "total")

ggplot(x)+
  geom_raster(aes(x,y,fill=value))+
  scale_fill_manual(values=c('light yellow','black'))+
  geom_sf(data=s,fill='grey',colour='transparent')+
  geom_sf(data=mcp,fill="transparent")+
  geom_text(data=df,x=-50,y=67,label=df$total)+
  facet_wrap(~month,nrow=2)+#,
  theme_classic()+
  scale_x_continuous(breaks = seq(-70,-50,10))+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold"))

ggsave("../output/maxent/paper_plots/maxkap_2d.png", height = 210, width = 297, units = "mm", dpi = 600)

----------------------

get data to plot maxkap binary by depth... 
```{r}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

```{r percentage cells above and below maxkap}
mthord <- c("mar",  "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
cumst1 <- read.csv("../output/maxent/paper_plots/cellsperlayer.csv", header = TRUE)

for (m in 1:length(mthord)){
  mth <- mthord[m]
  a <- read.csv(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_cellcount_bydepth_avg.csv"), header = TRUE, stringsAsFactors=FALSE)
  for (r in 1:nrow(a)){
    # a$Depth[r] <- gsub("b_avg_cloglog_", "", x = a$Depth[r])
    # d1 <- str_sub(a$Depth[r], end = 4)
    d1 <- a$asclayer[r]
	  for (ro in 1:nrow(cumst1)){
      #d2 <- str_sub(cumst1$depth[ro], end = 4)
	    d2 <- cumst1$depth[ro]
      if (d1 == d2){
          a$total_cells[r] <- cumst1$no_cells[ro]
      }
	  }
    a$p_cells[r] <- (a$prob_bin[r]/a$total_cells[r])*100
    a$Probability[r] <- 1
  }
    #a$asclayer <- as.numeric(a$asclayer)

  a2 <- as.data.frame(a$asclayer)
  a2$total_cells <- a$total_cells
  a2$prob_bin <- a$total_cells - a$prob_bin
  a2$p_cells <- (a2$prob_bin/a2$total_cells)*100
  a2$Probability <- 0
  colnames(a2)[1] <- "asclayer"

  b <- rbind(a, a2)
  colnames(b)[1] <- "Depth"

  write.csv(b, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_maxkap_dis_prob_cells.csv"), row.names = FALSE)
}

@@

based on Remi's code - maxkappa derrived habitat by depth

```{r}
require(data.table)
require(purrr)
require(lubridate)
require(tidyverse)
require(viridis)

filenames <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "_maxkap_dis_prob_cells.csv", recursive = TRUE,full.names = TRUE)

all <- map_dfr(filenames, function(x) fread(x) %>% 
                       mutate(Month=substr(basename(x),1,3))) %>% 
  mutate(Depth = factor(round(Depth,1)),
         Depth = factor(Depth,ordered = TRUE, levels = rev(levels(Depth))),
         Month=factor(months(parse_date_time(Month,"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))))

#make probability a factor - sam added this
all$Probability <- as.factor(all$Probability)

#make the plot
  ggplot(all) +
  geom_col(aes(Depth, p_cells, fill = Probability),width=1) +
  coord_flip()+
  facet_wrap(~Month,ncol=2)+
  labs(y = "% Ocean at Depth", x = "Depth (meters)")+
  scale_fill_manual(aesthetics = "fill", values=c('light yellow','black'))+
  theme_classic()+
  theme(legend.position = "bottom", axis.text.y = element_text(size=7), strip.background = element_blank()) +
  scale_x_discrete(breaks = c(dlst[1], dlst[5], dlst[10], dlst[15], dlst[20], dlst[25], dlst[30], dlst[35], dlst[40], dlst[47]))

ggsave("../output/maxent/paper_plots/maxkap_prob_by_depth.png", width = 210, height = 297, units = "mm", dpi = 600)
```

#get max and min depth layers based on max kappa
```{r}
kapd <- list.files("../output/maxent/paper_plots/prob_by_depth/" , pattern = "_maxkap_dis_prob_cells.csv", full.names = TRUE)

test <- read.csv(kapd[1])
test <- subset(test, Probability == 1) #just keep the presence cells
test <- test[order(test[, 1]),] #order by depth 
#now need to find the row in which a value first appears in prob_bin column
